\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-11 paper/draft.tex
Update transformations

>>>>

\heading{Context Transformation}
To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.

To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
Semantically, the context is a map from variable names to their values.
Thus, \sys creates an auxiliary hash table mapping names to transformed values.
Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.

%% FIXME: 
%% While user-defined global variables are stored in well-known locations,\footnote{
%%   For example, \ttt{globals} in JavaScript and \ttt{\_G} in Lua.
%% } traversing the global scope for built-in values is generally not possible.
%% To solve this problem, \sys collects such values by resolving well-known names hard-coded in a list;
%%   different lists exist for different environments and versions of the language.
%% Using this list, \sys creates a list of pointers to unmodified values. % upon startup.

Care must be taken with library-local variables. % that refer to library-specific information such as \ttt{\_\_name\_\_} in Python~\sx{bg1}.
These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
\sys solves this problem by leaving the value empty and deferring binding for later from within the scope of the library (see below).

\heading{Context Linking}
To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
The closure's body starts with a prologue of the form:
\begin{verbatim}
  pint = ctx.print
  error = ctx.error
  ...
\end{verbatim}
These statements shadow global variable names by redefining them as local ones.
The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
The prologue executes before everything else in the library.
% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.

Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
  these names are now bound to the correct library-local values.

\heading{Library Interface Transformation}
Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
The goal of the final transformation is to track activity at the boundary;
  for some analyses, \sys needs to also augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.
